The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-09 presentation/placenta_viviparous_presentation.Rnw
add section on makefiles

>>>>

\subsection{Using Make}

\begin{frame}{Makefile rules}
\centering
\includegraphics[keepaspectratio,height=0.8\textheight]{figures/default}
\end{frame}

\begin{frame}[fragile]{Common Options}
\tiny
\inputminted[firstline=8, lastline=36]{make}{../fastq/common_makefile}
\end{frame}

\begin{frame}[fragile]{FASTQC}
\inputminted[firstline=78, lastline=83]{make}{../fastq/common_makefile}
\end{frame}

\begin{frame}[fragile]{Trinity}
\tiny
\inputminted[firstline=211, lastline=222]{make}{../fastq/common_makefile}
\end{frame}

\begin{frame}[fragile]{Diamond}
\tiny
\inputminted[firstline=249, lastline=268]{make}{../fastq/common_makefile}
\end{frame}

\begin{frame}[fragile]{STAR Indexes}
\tiny
\inputminted[firstline=86, lastline=105]{make}{../fastq/common_makefile}
\end{frame}

\begin{frame}[fragile]{STAR}
\tiny
\inputminted[firstline=106, lastline=118]{make}{../fastq/common_makefile}
\end{frame}

\begin{frame}[fragile]{Cufflinks}
\tiny
\inputminted[firstline=43, lastline=60]{make}{../fastq/common_makefile}
\end{frame}
